---
title: "Homework 1"
author: Yiyao LI
output: github_document
---

This is my solution to HW1. 

```{r}
library(tidyverse)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df = 
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
)
```

Take the mean of each variable in my data frame.

```{r mean_pull_var}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec,))
mean(pull(prob1_df, factor_vec))
```

I can take mean of numbers and logical but not character or factor.

```{r try_numeric}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

## Problem 2

Write a short description of the penguins dataset

```{r}
data("penguins", package = "palmerpenguins")
```

the data in this dataset, including names / values of important variables

```{r}
names(penguins)
levels(pull(penguins,species))
levels(pull(penguins,island))
range(pull(penguins,bill_length_mm), na.rm = TRUE)
range(pull(penguins,bill_depth_mm), na.rm = TRUE)
range(pull(penguins,flipper_length_mm), na.rm = TRUE)
range(pull(penguins,body_mass_g), na.rm = TRUE)
levels(pull(penguins,sex))
range(pull(penguins,year))
```

the size of the dataset 

```{r}
nrow(penguins)
ncol(penguins)
```

the mean flipper length

```{r}
mean(range(pull(penguins,flipper_length_mm), na.rm = TRUE))
```



